Diagnosis_Vis

### 2023-04-17 Diagnosis_Vis.Rmd
Changed alpha level & fixed NAs in plot

# Broken up by disorder. 
ggplot(data=subset(Mothership, !is.na(Disorder_Type)), 
    mapping= aes(x=TxYear,y = stat(count),
                 group=Disorder_Type, fill=Disorder_Type)) +
  geom_density(adjust=1.5,alpha=.4) +
  facet_wrap(~Disorder_Type)+
  theme_classic()+
    theme(
      panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2),
      axis.text.x = element_text(angle = 45,hjust = 1),
      legend.position="none",
      panel.spacing = unit(0.1, "lines"),
      axis.ticks.x=element_blank(),
      panel.background=NULL) +
  labs(
    title = "Type of Disorders Treated at the Hospital Per Year",
    subtitle = "Broken Up By Dmotional vs Other Disorders") +
    xlab("Treatment Year") +
    ylab("Number of Patients With Disorder")

@@

```{r}
# without depression
ggplot(data=subset(No_depressy, !is.na(Disorder_Type)), 
    mapping= aes(x=TxYear,y = stat(count),
                 group=Disorder_Type, fill=Disorder_Type)) +
  geom_density(adjust=1.5,alpha=.4) +
  facet_wrap(~Disorder_Type)+
  theme_classic()+
    theme(
      panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2),
      axis.text.x = element_text(angle = 45,hjust = 1),
      legend.position="none",
      panel.spacing = unit(0.1, "lines"),
      axis.ticks.x=element_blank(),
      panel.background=NULL) +
  labs(
    title = "Type of Disorders Treated at the Hospital Per Year",
    subtitle = "Broken Up By Dmotional vs Other Disorders") +
    xlab("Treatment Year") +
    ylab("Number of Patients With Disorder")
```

>>>>

# Broken up by disorder. 
ggplot(data=subset(Mothership_Diag, !is.na(Disorder_Type)), 
    mapping= aes(x=TxYear,y = stat(count),
                 group=Disorder_Type, fill=Disorder_Type)) +
  geom_density(adjust=1.5,alpha=.6) +
  facet_wrap(~Disorder_Type)+
  theme_classic()+
    theme(
      panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2),
      axis.text.x = element_text(angle = 45,hjust = 1),
      legend.position="none",
      panel.spacing = unit(0.1, "lines"),
      axis.ticks.x=element_blank(),
      panel.background=NULL) +
  labs(
    title = "Type of Disorders Treated at the Hospital Per Year",
    subtitle = "Broken Up By Dmotional vs Other Disorders") +
    xlab("Treatment Year") +
    ylab("Number of Patients With Disorder")

@@

```{r}
# without depression
ggplot(data=subset(No_depressy, !is.na(Disorder_Type)), 
    mapping= aes(x=TxYear,y = stat(count),
                 group=Disorder_Type, fill=Disorder_Type)) +
  geom_density(adjust=1.5,alpha=.6) +
  facet_wrap(~Disorder_Type)+
  theme_classic()+
    theme(
      panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2),
      axis.text.x = element_text(angle = 45,hjust = 1),
      legend.position="none",
      panel.spacing = unit(0.1, "lines"),
      axis.ticks.x=element_blank(),
      panel.background=NULL) +
  labs(
    title = "Type of Disorders Treated at the Hospital Per Year",
    subtitle = "Broken Up By Dmotional vs Other Disorders") +
    xlab("Treatment Year") +
    ylab("Number of Patients With Disorder")
```
